Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-05 ms.tex
Formatting

The unresolved core X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).  Figure~\ref{fig:miller} shows our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm bol} \dot{M} c^2$ in Eddington units as a function of black hole mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric correction at X-ray energies appropriate for low luminosity AGN (\citealt{Ho08}).  We have averaged the accretion rate used in calculating $\langle L_X \rangle$ between the values for galaxies with core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles using the average value of the inner density slope $\Gamma$ as a function of black hole mass as fit from the \citet{LauerFaber+:2007a} galaxy sample, an exercise that results in the relationship $\Gamma = ...$. {\bf BDM: fill in}

The left panel of Figure \ref{fig:miller} is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$ typical of those estimated for low luminosity AGN (e.g., \citealt{Ho:2009a}), while the right panel luminosities are calculated instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison are the X-ray measurements (green stars) and upper limits (gray triangles) of early-type galaxies compiled by \citet{Miller+15} (cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit to the X-ray luminosity from \citet{Miller+15}, given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = XXX$  (see also \citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).  Yellow, teal, and red lines show the maximum accretion rates, respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]).

>>>>

The unresolved core X-ray luminosities of galactic nuclei provide a
powerful diagnostic of the SMBH accretion rates and how they vary
across different galaxy properties and SMBH masses (e.g.,
\citealt{Ho08} and references therein).  Figure~\ref{fig:miller} shows
our predictions for $\langle L_{X} \rangle =\epsilon_X \epsilon_{\rm
  bol} \dot{M} c^2$ in Eddington units as a function of black hole
mass, where $\epsilon_{\rm bol} = 0.1$ is the approximate bolometric
correction at X-ray energies appropriate for low luminosity AGN
(\citealt{Ho08}).  We have averaged the accretion rate used in
calculating $\langle L_X \rangle$ between the values for galaxies with
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density
profiles using the average value of the inner density slope $\Gamma$
as a function of black hole mass as fit from the
\citet{LauerFaber+:2007a} galaxy sample, an exercise that results in
the relationship $\Gamma = 0.3 \Mbheight^{-0.24}$.

The left panel of Figure \ref{fig:miller} is calculated assuming a
constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$
typical of those estimated for low luminosity AGN (e.g.,
\citealt{Ho:2009a}), while the right panel luminosities are calculated
instead assuming an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm
  edd}$ that depends on the Eddington ratio as predicted by some
models for radiatively inefficient accretion flows
(\citealt{Narayan&Yi95}; \citealt{Narayan+98}).  Shown for comparison
are the X-ray measurements (green stars) and upper limits (gray
triangles) of early-type galaxies compiled by \citet{Miller+15}
(cf.~\citealt{Gallo+10}).  A green line shows the best power-law fit
to the X-ray luminosity from \citet{Miller+15}, given by $\langle
L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with $\alpha = -0.2$ (see also
\citep{Zhang+09, Pellegrini10, Gallo+10} for similar conclusions).
Yellow, teal, and red lines show the maximum accretion rates,
respectively, for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]),
as set by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]), and as allowed by
Compton heating feedback (eq.~[\ref{eq:MdotC}]).

### 2015-03-05 windheat.tex
Formatting

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1 \label{eq:MDotSFH}\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1, \label{eq:EDotSFH}
\end{align}
resulting in a wind heating parameter of 
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
\end{align}
The mass return parameter will be
\begin{align}
\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
\end{align}
 % \begin{figure}
 % \includegraphics[width=\columnwidth]{NickPlot2.pdf}
 % \caption{\label{NickPlot2} Effective wind velocities for
 % nonstandard star formation histories.  The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.  The purple curve shows a recent drop in the star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.  Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively. }
 % \end{figure}
We estimate the stellar wind heating provided by the {\it average}
star formation history of galaxies of a given $\Mbh$ using the results
of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
star formation histories in \citet{MosterNaab+:2013a} are in terms of
halo mass. For a given $\Mbh$ we assign the halo mass whose star
formation history would produce a bulge consistent with the
$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A slight complication occurs for the largest mass halos, where much of the $z=0$ stellar mass has been acquired through accretion of satellite halos rather than {\it in situ} star formation.  To accomodate this, we use analytic fits for mass accretion histories $A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}, and replace $S(t) \rightarrow S(t)+A(t)$ in Eqs. \ref{eq:MDotSFH} and \ref{eq:EDotSFH}.

>>>>

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1 \label{eq:MDotSFH}\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1, \label{eq:EDotSFH}
\end{align}
resulting in a wind heating parameter of 
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
\end{align}
The mass return parameter will be
\begin{align}
\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
\end{align}
 % \begin{figure}
 % \includegraphics[width=\columnwidth]{NickPlot2.pdf}
 % \caption{\label{NickPlot2} Effective wind velocities for
 % nonstandard star formation histories.  The black curve shows, for reference, $v_{\rm w}$ calculated using the halo-averaged $S(t)$.  Other colors show the effective wind velocities $\mathcal{V}_{\rm w}$ computed using convolved star formation histories $\mathcal{S}(t)$.  The purple curve shows a recent drop in the star formation rate, i.e. $t_{\rm scale}=10^6~{\rm yr}$.  The blue and red curves show $t_{\rm scale}=10^7~{\rm yr}$ and $t_{\rm scale}=10^8~{\rm yr}$, respectively; longer scale times look quite similar to the red curves.  Dashed, dotted, and dot-dashed line styles show star formation rates that have declined to fractions $\epsilon = 0.001$, $\epsilon = 0.1$, and $\epsilon = 0.3$ of their halo-averaged values, respectively. }
 % \end{figure}
We estimate the stellar wind heating provided by the {\it average}
star formation history of galaxies of a given $\Mbh$ using the results
of \citet[eqs.~17-20]{MosterNaab+:2013a}.  Note that the
star formation histories in \citet{MosterNaab+:2013a} are in terms of
halo mass. For a given $\Mbh$ we assign the halo mass whose star
formation history would produce a bulge consistent with the
$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.  A
slight complication occurs for the largest mass halos, where much of
the $z=0$ stellar mass has been acquired through accretion of
satellite halos rather than {\it in situ} star formation.  To
accomodate this, we use analytic fits for mass accretion histories
$A(t)$, also taken from \citet[eqs.~21-23]{MosterNaab+:2013a}. We
assume that accreted systems will have the same star formation history
as the host up until the moment of accretion. To find the total mass
(energy) injection including the contributions of accreted stars we
convolve the specific mass (energy) injection rate with the accretion
history $A(t)$.  The total mass ($\Mdot'(t)$) and energy
($\dot{E}'(t)$) rates will be given by

\begin{align}
\Mdot '(t)&=\Mdot(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\Mdot(t_{\rm acc})}
{\int_{0}^{t_{\rm acc}} S(t_1) dt_1} {\rm dt_{ acc}}.\\
\dot{E}'(t)&=\dot{E}(t)+\int_{0}^{t} A(t_{\rm acc}) \frac{\dot{E}(t_{\rm acc})}
{\int_{0}^{t_{\rm acc}} S(t') dt_1} {\rm dt_{acc}}.
\end{align}

The corresponding wind heating parameter $v_w'$ and mass return
parameter, $\eta'$, will be given by

\begin{align}
\eta'&=\frac{\Mdot'(t)}{\int_0^t S(t_1) {\rm d}t_1+\int_0^t A(t_1) {\rm
    d}t_1} \th\\
v_w'&=2 \frac{\dot{E}'(t)}{\Mdot'(t)}
\end{align}
